The Effects of the NBA COVID Bubble on the NBA Playoffs

### 2020-11-10 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd

Some studies focus less on shooting and more on scoring differences and other metrics.
For example, @Greer focuses his study on the influence of spectator booing on 
Home-court advantage in basketball. The three methods of performance used
in this study were scoring, violations and turnovers. This study was conducted 
using the men’s basketball programs at two large universities. The study finds that
social support, like booing, is an important contributor to home-court advantage. 
Greer explains, whether the influence is greater on visiting team performance or
referee calls is less clear. However, the data does seem to lean slightly in
favor of affecting visiting team performance. One study conducted by @Harville studied the
effect of home-court advantage using the 1991-1992 college basketball season. 
Unlike the NBA, it is not uncommon to have a few games played at neutral sites
during the college basketball season. This allowed them to construct two samples,
one of home teams and one of neutral teams. They formulate their study as a 
regression equation predicting the expected difference in score for home teams. 
They set up their study to find if the home teams won games by more points when 
they had home-court advantage vs. when playing at neutral court. This study 
succeeds in proving that home-court advantage exists.

@@

```{r table, echo = FALSE}
knitr::kable(resultsfinal, caption = 'The results from the 9 statistical tests', align = "cccccc", booktabs = TRUE)
```

>>>>

Some studies focus less on shooting and more on scoring differences and other metrics.
For example, @Greer focuses his study on the influence of spectator booing on 
home-court advantage in basketball. The three methods of performance used
in this study were scoring, violations and turnovers. This study was conducted 
using the men’s basketball programs at two large universities. The study finds that
social support, like booing, is an important contributor to home-court advantage. 
Greer explains, whether the influence is greater on visiting team performance or
referee calls is less clear. However, the data does seem to lean slightly in
favor of affecting visiting team performance. One study conducted by @Harville studied the
effect of home-court advantage using the 1991-1992 college basketball season. 
Unlike the NBA, it is not uncommon to have a few games played at neutral sites
during the college basketball season. This allowed them to construct two samples,
one of home teams and one of neutral teams. They formulate their study as a 
regression equation predicting the expected difference in score for home teams. 
They set up their study to find if the home teams won games by more points when 
they had home-court advantage vs. when playing at neutral court. This study 
succeeds in proving that home-court advantage exists.

@@

```{r table, echo = FALSE}
knitr::kable(resultsfinal, caption = 'The results from the 9 tests', align = "cccccc", booktabs = TRUE)
```
